---
author: "Li"
date: "2019-04-19"
categories:
- Go
description: ""
featured: a.jpg
featuredalt: Pic 2
featuredpath: date
linktitle: ""
title: Life will change
type: post

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


It's not a game
I'm not a robot
A.I. challenging you
I'm not a Phantom
I'm in your face and
I'm here to see it through
Right before your eyes
Watch us multiply
Come to claim our rights
It's time
As our power grows
Tryin' to stop us shows
Might as well go try'n
Stop time

So you know that we're out there
Swatting lies in the making
Can't move fast without breaking
Can't hold on or life won't change
And our voices ring out Yeah
Took the Mask off to feel free
Fought it out in the debris
Now we know that life will change

更多更詳盡歌詞 在 ※ Mojim.com　魔鏡歌詞網 
Ain't it a shame
I'm not a figment
Of your ailing old mind
I'm just as real as
I'm just as dangerous
As you will soon find
A taste of your own meds
Fire in every breath
Fire inside your head
Your heart
And as your crippled brain
Tries to fight in vain
Your empire will fall apart

And you'll know that we're out there
Swatting lies in the making
Your empire for the taking
Can't hold on or life won't change
And our voices ring out Yeah
Took the mask off to feel free
Fought it out in the debris
Now we know that life will change



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
